---
title: "p8105_hw1_September28_kkc2146"
output: html_document
---

# HW1 Problem 1
### The purpose of this HW problem is to emphasize variable types and introduce coercion, some awareness of how R treats numeric, character, and factor variables 

The code chunk below creates a data frame comprised of: 
* a random sample size of 10 from a standard normal distribution 
* a logical vector indicating whether elements of the sample are greater than 0 
* a character vector of length 10 
* a factor vector of length 10, with 3 different factor "levels" 

```{r Problem 1}
library(tidyverse)
tibble(
  x = rnorm(10), 
  norm_samp = rnorm(10, mean = 1),
  norm_samp_pos = norm_samp > 0,
  char_vector = (c("fall", "is", "here","finally","and", "the", "leaves", "will","be", "pretty")),
  y <- factor(c("1", "1", "1", "1", "1", "1", "1", "1", "2", "3"))
)
```

# HW 1 Problem 2 
This problem focuses the use of inline R code, plotting, and the behavior of ggplot for variables of different types.

install.packages("palmerpenguins")

library('palmerpenguins')

```{r}
data("penguins", package = "palmerpenguins")
```



